---
title: "Data Science and Analytics 2022"
author: "Hatice Özgül BİLİCİ"
output: html_document
---

<style type="text/css">
  body{
  font-size: 11pt;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

<!--IMPORTANT!!!!! Please fill out the sections that say:"write your code here"-->
<!--6. For every step above, write down one or two sentences description-->

<br>

```{r echo=T, results='hide', warning=FALSE, message=FALSE}
  
  # Import libraries here
  library(ggplot2)
  library(tidyverse)
  library(dplyr)
  library(plyr)
```

<br>

### 1) Download the dataset from the link below and import the dataset to R as a dataframe named ***'alcohol_data'***.

<br>

***https://www.kaggle.com/datasets/whenamancodes/alcohol-effects-on-study***

<br>
```{r}
  alcohol_data <- read.csv("Maths.csv",sep=",")
```

<br>

### 2)

#### A) Create a new dataframe as ***'alcohol_data_small'*** from ***'alcohol_data'*** by choosing at least 5 columns (at least one factor and one numeric). 

<br>

```{r}
  alcohol_data_small <- alcohol_data [, c(2,3,4,6,9,10,11,12,13,19,25,31)]
```

<br>

#### B) Check and ***re-format*** column/ variable types (factor, charecter, date, integer etc).

<br>

```{r}
  str(alcohol_data_small)
```

```{r}
  alcohol_data_small <- transform(alcohol_data_small ,
                                  freetime = as.factor(freetime),
                                  traveltime = as.factor(traveltime)
                                  )
```

```{r} 
  str(alcohol_data_small)

```
<br>

#### C) By using the given dictionary in kaggle, rename the variables as a more detailed version (e.g. 'F' => 'Female').

<br>
```{r}
  alcohol_data_small <- transform(alcohol_data_small,
                                  sex = as.factor(mapvalues(sex , c("F","M") , c("Female" , "Male"))),
                                  address = as.factor(mapvalues(address , c("U","R") , c("Urban" , "Rural"))),
                                  Pstatus = as.factor(mapvalues(Pstatus , c("T", "A") , c("Together", "Apart"))))
                                  
                                  
                                  
```

```{r}
summary(alcohol_data_small)
```
<br>

### 3) 

#### A) Use ***filter***, ***arrange***, ***select*** to manage your data.
<br>

```{r}
    df <- alcohol_data_small %>% 
                          filter(sex == "Male" & address == "Rural" & age>15)%>%
                          select(sex, address, age)%>%
                          arrange(age)
    df
```


<br>

#### B) Use ***mutate*** or ***transmute*** to create a new dataframe and save it as ***'new_data.csv'*** in your current working directory.

<br>

```{r}
  df1 <- alcohol_data_small%>%
                              mutate(newage = age+mean(age))
  head(df1[c(2)])
  
```
```{r}
write.csv(x = df1, file = "new_alcohol_data_small.csv", row.names = FALSE)
```
<br>

### 4) Use ***'alcohol_data_small'*** dataframe and ggplot2 library to draw the following plots.

<br>

#### A) Draw a ***histogram*** and a ***bar chart*** for any variables and comment about shape and frequency. 

<br>



```{r}
  ggplot(alcohol_data_small, aes(G1, fill=freetime)) + 
  geom_histogram(position="identity", binwidth=2, color="black") +
  facet_grid(freetime ~ .) + 
  ggtitle("G1 Skore by Freetime") +
  xlab("G1 Skore") + 
  ylab("Count")

```

The grades of those with the least free time seem to be the lowest. However, a linear relationship between free time and G1 score cannot be decisively found.

```{r}

  
  ggplot(alcohol_data_small, mapping = aes(x=sex, fill=traveltime)) + 
  geom_bar()+
  labs(title = "Travel time BarChart by Gender", x="Sex", y="Count")
```
As can be seen, the number of those who have home to school travel time <15 is much higher in Female.
-home to school travel time (numeric: 1 - <15 min., 2 - 15 to 30 min., 3 - 30 min. to 1 hour, or 4 - >1 hour)-

<br>

#### B) Draw a ***boxplot*** and comment about the distribution and outliers. 

<br>


```{r ,warning=FALSE}
  ggplot(alcohol_data_small, mapping = aes(x = freetime, y = age , fill=freetime)) + 
  geom_boxplot(outlier.size = 4 ,outlier.shape = 20)+
  stat_summary(fun.y = "mean",shape=4,size=0.5)+
  labs(title = "Ages by Free Time Hours", x="freetime", y="age")
```

As the age decreases, we can comment that the free time spent by the student increases. However, there are also outliers at high ages. (can be ignored)

<br>
<br>