---
title: "Data Science and Analytics 2022"
author: "Hatice Özgül Bilici"
date: "2022-11-17"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r echo=T, results='hide', warning=FALSE, message=FALSE}
  library(ggplot2)
  library(tidyverse)
  library(dplyr)
  library(plyr)
  library(caret)
  library(corrplot)
  library(ROCR)
  library(Rcpp)
  library(gmodels)
  library(pROC)
  library(InformationValue)
  library(factoextra)

```


```{r}
  setwd("C:/Users/ASUS/Desktop/Data")
```
# DATA DOWNLOAD

```{r}
  moledata <- read.csv("mole_dataset.csv",sep=",")
```
# EDIT DATA VARIABLES

```{r}
moledata$image_id <- NULL
moledata$clin_size_long_diam_mm <- NULL
moledata$sex <- NULL
moledata$X <- NULL

```

```{r}
  moledata$benign_malignant <-  factor(moledata$benign_malignant)
  summary(moledata)
```
# CORRELATION MATRIX


```{r}

moledata <- na.omit(moledata)
cor <- cor(moledata[,3:9])
cp <- corrplot(cor,method = "ellipse")

```

<br>

There is a strong correlation for dark colors and a weak correlation for light colors.

<br>

# Logistic Regression Model


```{r}
  bdata <- moledata[which(moledata$benign_malignant == "benign"), ] # tüm 1'ler  
  mdata <- moledata[which(moledata$benign_malignant == "malignant"), ]
  nrow(bdata)
  nrow(mdata)
  
  
  set.seed(100)
  
  bdata_training_rows <- sample(1:nrow(bdata),  size= 0.60*nrow(mdata))
  
  mdata_training_rows <- sample(1:nrow(mdata),  size= 0.60*nrow(mdata))
  
  training_b <- bdata[bdata_training_rows, ] 
  training_m <- mdata[mdata_training_rows, ]

  trainingData <- rbind(training_b, training_m)
  
  testData <-rbind(bdata[-bdata_training_rows,],mdata[-mdata_training_rows,])

  table(testData$benign_malignant)
  
  
  LRmod <- glm(benign_malignant~ ., data=trainingData, family=binomial) 
  summary(LRmod)

```
<br>

The age_approx, corners, and green variables have a significant impact on mole analysis. However, other variables do not have a significant effect on mole-analysis.

<br>
# Confusion Matrix

```{r}
predict <- predict(LRmod , testData ,type="response")

ConfMatrix <- confusionMatrix(testData$benign_malignant , predict)
ConfMatrix

accurance <- (ConfMatrix[1,1] + ConfMatrix[2,2])/ sum(ConfMatrix)
```

# ROC Curve

```{r}
rocMod <- roc(testData$benign_malignant ~ predict)

plot(rocMod)

rocMod

```

# APPLY PCA

```{r }

PCAmole <- prcomp(moledata[,-10] , scale=TRUE,center = TRUE)
summary(PCAmole)

```
# DRAW PCA

```{r }
PCAmole.var <- PCAmole$sd^2
PCAmolePercent <- PCAmole.var/sum(PCAmole.var) * 100
dev.new()
```

```{r }
 barplot(PCAmolePercent, xlab='PC', ylab='Percent Variance', names.arg=1:length(PCAmolePercent), las=1, ylim=c(0, max(PCAmolePercent)), col='blue')

```


```{r }
fviz_eig(PCAmole)
```